Learning STRIPS action models with classical planning

### 2017-10-13 doc/icaps-18/strips-learning.tex
first evaluation results added

Likewise, we assume that each action in $A$ is instantiated from a STRIPS operator schema. Figure~\ref{fig:stack} shows the STRIPS operator schema that corresponds to the {\em stack} action from the blocksworld~\cite{slaney2001blocks} represented in PDDL.
\begin{figure}[hbt]
\begin{footnotesize}
\begin{verbatim}
(:action stack
  :parameters (?x1 ?x2 - object)
  :precondition (and (holding ?x1) 
                     (clear ?x2))
  :effect (and (not (holding ?x1)) 
               (not (clear ?x2))
               (clear ?x1) 
               (handempty) 
               (on ?x1 ?x2)))
\end{verbatim}
\end{footnotesize}
 \caption{\small Example of a STRIPS operator schema that corresponds to the {\em stack} action from the blocksworld represented in PDDL.}
\label{fig:stack}
\end{figure}

@@

\vspace{0.3cm}

\begin{subfigure}{.3\textwidth}
\begin{small}
{\tt ;;; Plan $\pi_1$}
\begin{verbatim}
0: (unstack A B)
1: (putdown A)
2: (unstack B C)
3: (stack B A)
4: (unstack C D)
5: (stack C B)
6: (pickup D)
7: (stack D C)
\end{verbatim}
\end{small}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
{\small\tt ;;; Label $\sigma_1=(s_0^1,s_{n}^1)$}
\begin{lstlisting}[mathescape]
\end{lstlisting}
\begin{tikzpicture}[node distance = 0mm, block/.style args = {#1,#2}{fill=#1,text width=#2,shape=square}]
\node (initD) [draw]{D};
\node (initC) [draw, above=of initD.north]{C};
\node (initB) [draw, above=of initC.north]{B};
\node (initA) [draw, above=of initB.north]{A};
\draw[thick] (-1,-0.25) -- (2.5,-0.25);

@@

\section{Learning STRIPS action models with planning}
Our approach for addressing a learning task $\Lambda$, $\Lambda'$ or $\Lambda''$, is compiling it into a classical planning task with conditional effects $P_{\Lambda}$, $P_{\Lambda'}$ or $P_{\Lambda''}$. The intuition behind these compilations is that a solution to the resulting classical planning task is a sequence of actions that:
\begin{enumerate}
\item Programs the STRIPS action model $\Xi$. For each $\xi\in\Xi$, the solution plan determines the literals that belong to the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ sets.
\item Validates the programmed the STRIPS action model $\Xi$ using the available input knowledge ($\Pi$, if available, and the given set of labels $\Sigma$).  At every learning example {\small $1\leq t\leq \tau$}, then $\Xi$ is used to produce a final state $s_{n}^t$ starting from the corresponding initial state $s_0^t$. If information about the corresponding plan $\pi_t$ is available, then it is used to constrain the validation of the programmed STRIPS action model $\Xi$.
\end{enumerate}

Figure~\ref{fig:plan} shows a classical plan for solving a learning task of the $\Lambda$ class. The shown classical plan programs and validates the operator schema {\tt\small stack} from the blocksworld using the plan $\pi_1$ and label $\sigma_1$ shown in Figure~\ref{fig:lexample}. In particular the steps $[0,8]$ are actions for programming the preconditions of the operator, steps $[9,13]$ are actions for programming the operator effects and steps $[14,22]$ are actions for validating the programmed operator. The details of the compilation are given in the remaining of the section.

\begin{figure}[hbt]
\begin{footnotesize}
\begin{verbatim}
     0 : (program_pre_clear_stack_var1)
     1 : (program_pre_handempty_stack_)
     2 : (program_pre_holding_stack_var2)
     3 : (program_pre_on_stack_var1_var1)
     4 : (program_pre_on_stack_var1_var2)
     5 : (program_pre_on_stack_var2_var1)
     6 : (program_pre_on_stack_var2_var2)
     7 : (program_pre_ontable_stack_var1)
     8 : (program_pre_ontable_stack_var2)
     9 : (program_eff_clear_stack_var1)
    10 : (program_eff_clear_stack_var2)
    11 : (program_eff_handempty_stack_)
    12 : (program_eff_holding_stack_var1)
    13 : (program_eff_on_stack_var1_var2)
    14 : (apply_unstack a b i1 i2)
    15 : (apply_putdown a i2 i3)
    16 : (apply_unstack b c i3 i4)
    17 : (apply_stack b a i4 i5)
    18 : (apply_unstack c d i5 i6)
    19 : (apply_stack c b i6 i7)
    20 : (apply_pickup d i7 i8)
    21 : (apply_stack d c i8 i9)
    22 : (validate_1)
\end{verbatim}
\end{footnotesize}
 \caption{\small Example of a plan for programing and validating the operator schema unstack using the plan $\pi_1$ and label $\sigma_1$ shown in Figure~\ref{fig:lexample}.}
\label{fig:plan}
\end{figure}

To formalize our compilations we first define {\small $1\leq t\leq \tau$} classical planning instances $P_t=\tup{F,\emptyset,I_t,G_t}$, one for each leaning example, that belong to the same planning frame (i.e. same fluents and actions and differ only in the initial state and goals). The set of fluents $F$ is built instantiating the predicates in $\Psi$ with the set of different objects appearing in the examples. Formally $\Omega=\{o|o\in \bigcup_{\small 1\leq t\leq \tau} obj(s_0^t)\}$, where $obj$ is a function that returns the set of objects that appear in a fully specified state. The set of actions, $A=\emptyset$, is empty because the action model is unknown. Finally, the initial state $I_t$ is given by the state $s_0^t\in \sigma_t$ while goals $G_t$, are defined by the state $s_n^t\in \sigma_t$.

@@

Given a learning task $\Lambda''=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda''}=\tup{F_{\Lambda''},A_{\Lambda''},I_{\Lambda''},G_{\Lambda''}}$ such that:
\begin{itemize}
\item $F_{\Lambda''}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model $pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$, for every $f\in F_v$ and $\xi \in \Xi$). If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect in the STRIPS operator schema $\xi\in \Xi$. 
\item A fluent $mode_{prog}$ indicating whether the operator schema are being programmed or they are already programmed operators so are being validated in the learning examples. 
\item Fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the learning example where the programmed action model is being validated.
\end{itemize}
\item $I_{\Lambda''}$, contains the fluents from $F$ that encode $s_0^1$ (i.e. the initial state of the first learning example), every fluent $pre_f(\xi)\in F_{\Lambda}$ (our compilation assumes that initially, any operator schema, contains all the possible preconditions, no negative effect and no positive effect) and $mode_{prog}$. 
\item $G_{\Lambda''}=\{test_t\}$, {\small $1\leq t\leq \tau$}, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda''}$ contains actions of three different kinds:
\begin{enumerate}
\item The actions for programming the operator schema. This set includes:
\begin{itemize}
\item The actions for removing a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programPre_{f,\xi}})=&\{\neg del_{f}(\xi),\neg add_{f}(\xi),\\
& mode_{prog},pre_{f}(\xi)\},\\    
\cond(\mathsf{programPre_{f,\xi}})=&\{\emptyset\}\rhd\{\neg pre_{f}(\xi)\}.
\end{align*}
\end{small}

\item The actions for adding a {\em negative} or {\em positive} effect $f\in F_v$ to the action schema $\xi\in\Xi$.

@@

For instance, these actions define that if an operator is programmed with the precondition $holding(v_1)\in F_v$ it {\em implies} ($\implies$) that $holding(block_1)\in F$ has to be true in the current state if the operator binds the variable object $v_1\in\Omega_v$ with the regular object $block_1\in\Omega$. The operator binding is done implicitly by order of appearance, i.e. the variables in $pars(\xi)$ are bound to the objects in $\omega$ appearing in the same position.

@@

\begin{proof}[Proof sketch]
Once the preconditions of an operator schema $\Xi$ are programmed, they cannot be altered. The same happens with the positive and negative effects that define an operator schema $\xi \in \Xi$ (besides they can only be programmed after the operator preconditions are programmed, because of the preconditions of the $programPre_{f,\xi}$ actions). Furthermore, once the operator schema are programmed they can only be applied because of the value of the $mode_{prog}$ fluent. The only way of achieving a goal $\{test_t\}$,{\small $1\leq t\leq \tau$} is by executing an applicable sequence of programmed operator schema that achieves the final state defined by the associated label $\sigma_t$, starting from the initial defined in this same label. If this is done for all the input examples of the learning task (for all the labels $\sigma_t$, {\small $1\leq t\leq \tau$}), it means that the programmed action model $\Xi$ is compliant with all the learning input knowledge and hence, it is a solution to the action model learning task.
\end{proof}

@@

\section{Evaluation}
We evaluated our learning approach for different amounts of available input knowledge. In all the experiments the compilation is solved using the SAT-based classical planner {\sc Madagascar}~\cite{rintanen2014madagascar} given its ability to deal with planning instance highly populated with dead-ends.

@@

\subsection{Learning action models from example plans}
Here we assess the performance of our learning approach when addressing the $\Lambda$ learning task. The quality of the learned models is quantified using the cardinality of the {\em symmetric difference} between the set of preconditions, negative and positive effects (1), in the learned model and (2), in the actual models taken as reference.

Last but not least, collecting {\em informative} examples for learning planning action models is challenging open issue. Planning actions include preconditions that are only satisfied by specific sequences of actions, and often, with a low probability of being chosen by chance~\cite{fern2004learning}. In addition, motivated by the success of recent algorithms for exploring planning tasks~\cite{geffner:novelty:IJCAI17}, we do not assume that a learning set of plans is given apriori but instead, we autonomously collect the learning examples.

\begin{table}[hbt!]
\begin{footnotesize}
\begin{tabular}{cc}

\end{tabular}
\end{footnotesize}
\caption{\small Mean error and standard deviation of the learned models.}
  \label{tab:eplans}
\end{table}

Table~\ref{tab:eplans} shows the mean error and standard deviation of the learned models with respect to the actual action models. The standard deviation provides a measure of how this error is distributed among the different operators in the domain. If this deviation is 0 it means that is equally distributed in all the domain operators.

\subsection{Learning action models from example states}
When the set of input planning task is not available the {\em symmetric difference} is not an acceptable measure for evaluating the quality of the learned models. The reason is that, in this situation, the planner determines also the actions that must satistying the input labels so actions can reformulated and still be compliant with the learning examples. For instance a blocksworld can be learned where the operator {\small\tt stack} is defined with the preconditions and effects of the {\small\tt unstack} operator and vice versa.

With this regard, the Table~\ref{tab:noplans} shows the planning time and number of steps required to build a set of action models compliant with the input examples.

\begin{table}[hbt!]
\begin{footnotesize}
\begin{tabular}{cc}

\end{tabular}
\end{footnotesize}
\caption{\small Planning time and number of steps required to build a set of action models compliant with the input examples.}
  \label{tab:noplans}
\end{table}

@@

>>>>

Likewise, we assume that actions are instantiated from a STRIPS operator schema. Figure~\ref{fig:stack} shows the STRIPS operator schema that corresponds to the {\em stack} action from the blocksworld~\cite{slaney2001blocks} represented in PDDL.
\begin{figure}[hbt]
\begin{footnotesize}
\begin{verbatim}
(:action stack
  :parameters (?x1 ?x2 - object)
  :precondition (and (holding ?x1) 
                     (clear ?x2))
  :effect (and (not (holding ?x1)) 
               (not (clear ?x2))
               (clear ?x1) 
               (handempty) 
               (on ?x1 ?x2)))
\end{verbatim}
\end{footnotesize}
 \caption{\small Example of a STRIPS operator schema that corresponds to the {\em stack} action from the blocksworld represented in PDDL.}
\label{fig:stack}
\end{figure}

@@

\vspace{0.5cm}

\begin{subfigure}{.25\textwidth}
\begin{small}
{\tt ;;; Plan $\pi_1$}
\begin{verbatim}
0: (unstack A B)
1: (putdown A)
2: (unstack B C)
3: (stack B A)
4: (unstack C D)
5: (stack C B)
6: (pickup D)
7: (stack D C)
\end{verbatim}
\end{small}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
{\small\tt ;;; Label $\sigma_1=(s_0^1,s_{n}^1)$}
\begin{lstlisting}[mathescape]
\end{lstlisting}
\vspace{0.1cm}
\begin{tikzpicture}[node distance = 0mm, block/.style args = {#1,#2}{fill=#1,text width=#2,shape=square}]
\node (initD) [draw]{D};
\node (initC) [draw, above=of initD.north]{C};
\node (initB) [draw, above=of initC.north]{B};
\node (initA) [draw, above=of initB.north]{A};
\draw[thick] (-1,-0.25) -- (2.5,-0.25);

@@

\section{Learning STRIPS action models with planning}
Our approach for addressing a learning task $\Lambda$, $\Lambda'$ or $\Lambda''$, is compiling it into a classical planning task with conditional effects $P_{\Lambda}$, $P_{\Lambda'}$ or $P_{\Lambda''}$. The intuition behind these compilations is that a solution to the resulting classical planning task is a sequence of actions that:
\begin{enumerate}
\item Programs the STRIPS action model $\Xi$. For each $\xi\in\Xi$, the solution plan determines the literals that belong to the $pre(\xi)$, $del(\xi)$ and $add(\xi)$ sets.
\item Validates the programmed the STRIPS action model $\Xi$ using the given input knowledge ($\Pi$ if available, and the given set of labels $\Sigma$).  At every learning example {\small $1\leq t\leq \tau$}, then $\Xi$ is used to produce a final state $s_{n}^t$ starting from the corresponding initial state $s_0^t$. If information about the corresponding plan $\pi_t$ is available, then it is used to constrain the validation of the programmed STRIPS action model $\Xi$.
\end{enumerate}

Figure~\ref{fig:plan} shows a classical plan for solving a learning task of the $\Lambda$ class. The shown classical plan programs and validates the operator schema {\tt\small stack} from the blocksworld using the plan $\pi_1$ and label $\sigma_1$ shown in Figure~\ref{fig:lexample}. In particular the steps $[0,8]$ are the actions for programming the preconditions of the operator, steps $[9,13]$ are the actions for programming the operator effects and steps $[14,22]$ are the actions for validating the programmed operator. The details of the compilation are given in the remaining of the section.

\begin{figure}[hbt]
\begin{scriptsize}
\begin{verbatim}
     0 : (program_pre_clear_stack_v1)
     1 : (program_pre_handempty_stack)
     2 : (program_pre_holding_stack_v2)
     3 : (program_pre_on_stack_v1_v1)
     4 : (program_pre_on_stack_v1_v2)
     5 : (program_pre_on_stack_v2_v1)
     6 : (program_pre_on_stack_v2_v2)
     7 : (program_pre_ontable_stack_v1)
     8 : (program_pre_ontable_stack_v2)
     9 : (program_eff_clear_stack_v1)
    10 : (program_eff_clear_stack_v2)
    11 : (program_eff_handempty_stack)
    12 : (program_eff_holding_stack_v1)
    13 : (program_eff_on_stack_v1_v2)
    14 : (apply_unstack a b i1 i2)
    15 : (apply_putdown a i2 i3)
    16 : (apply_unstack b c i3 i4)
    17 : (apply_stack b a i4 i5)
    18 : (apply_unstack c d i5 i6)
    19 : (apply_stack c b i6 i7)
    20 : (apply_pickup d i7 i8)
    21 : (apply_stack d c i8 i9)
    22 : (validate_1)
\end{verbatim}
\end{scriptsize}
 \caption{\small Example of a plan for programing and validating the operator schema unstack using the plan $\pi_1$ and label $\sigma_1$ shown in Figure~\ref{fig:lexample}.}
\label{fig:plan}
\end{figure}

To formalize our compilations we first define {\small $1\leq t\leq \tau$} classical planning instances $P_t=\tup{F,\emptyset,I_t,G_t}$, one for each leaning example, that belong to the same planning frame (i.e. same fluents and actions and differ only in the initial state and goals). The set of fluents $F$ is built instantiating the predicates in $\Psi$ with the set of different objects appearing in the input learning examples. Formally $\Omega=\{o|o\in \bigcup_{\small 1\leq t\leq \tau} obj(s_0^t)\}$, where $obj$ is a function that returns the set of objects that appear in a fully specified state. The set of actions, $A=\emptyset$, is empty because the action model is unknown. Finally, the initial state $I_t$ is given by the state $s_0^t\in \sigma_t$ while goals $G_t$, are defined by the state $s_n^t\in \sigma_t$.

@@

Given a learning task $\Lambda''=\tup{\Psi,\Sigma}$ the compilation outputs a classical planning task $P_{\Lambda''}=\tup{F_{\Lambda''},A_{\Lambda''},I_{\Lambda''},G_{\Lambda''}}$ such that:
\begin{itemize}
\item $F_{\Lambda''}$ extends $F$ with:
\begin{itemize}
\item Fluents representing the programmed action model $pre_f(\xi)$, $del_f(\xi)$ and $add_f(\xi)$, for every $f\in F_v$ and $\xi \in \Xi$). If a fluent $pre_f(\xi)/del_f(\xi)/add_f(\xi)$ holds, it means that $f$ is a precondition/negative effect/positive effect in the STRIPS operator schema $\xi\in \Xi$. 
\item A fluent $mode_{prog}$ indicating whether the operator schema are being programmed or they are already programmed operators, so are being validated in the learning examples. 
\item Fluents $\{test_t\}_{1\leq t\leq \tau}$, indicating the learning example where the programmed action model is being validated.
\end{itemize}
\item $I_{\Lambda''}$, contains the fluents from $F$ that encode $s_0^1$ (i.e. the initial state of the first learning example), every fluent $pre_f(\xi)\in F_{\Lambda}$ (note that our compilation assumes that initially, any operator schema, contains all the possible preconditions, no negative effect and no positive effect) and the $mode_{prog}$ set to true. 
\item $G_{\Lambda''}=\{test_t\}$, {\small $1\leq t\leq \tau$}, indicates that the programmed action model is validated in all the learning examples.
\item $A_{\Lambda''}$ contains actions of three different kinds:
\begin{enumerate}
\item The actions for programming the operator schema. This set includes:
\begin{itemize}
\item The actions for removing a {\em precondition} $f\in F_v$ from the action schema $\xi\in\Xi$.

\begin{small}
\begin{align*}
\hspace*{7pt}\pre(\mathsf{programPre_{f,\xi}})=&\{\neg del_{f}(\xi),\neg add_{f}(\xi),\\
& pre_{f}(\xi), mode_{prog}\},\\    
\cond(\mathsf{programPre_{f,\xi}})=&\{\emptyset\}\rhd\{\neg pre_{f}(\xi)\}.
\end{align*}
\end{small}

\item The actions for adding a {\em negative} or a {\em positive} effect $f\in F_v$ to the action schema $\xi\in\Xi$.

@@

The binding of the operator schema is done implicitly by order of appearance, i.e. the variables in $pars(\xi)$ are bound to the objects in $\omega$ appearing in the same position. To illustrate this, Figure~\ref{fig:compilation} shows the PDDL encoding of the action for applying an already programmed operator schema $stack$.

@@

\begin{proof}[Proof sketch]
Once the preconditions of an operator schema $\Xi$ are programmed, they cannot be altered. The same happens with the positive and negative effects that define an operator schema $\xi \in \Xi$ (besides they can only be programmed after the operator preconditions are programmed, because of the preconditions in the $programPre_{f,\xi}$ actions). Furthermore, once the operator schema are programmed they can only be applied because of the value of the $mode_{prog}$ fluent. To solve the classical planning task $P_{\Lambda''}$, the only way of achieving a goal $\{test_t\}$,{\small $1\leq t\leq \tau$} is by executing an applicable sequence of programmed operator schema that achieves the final state $s_n^t$ defined by the associated label $\sigma_t$, starting from the initial $s_0^t$ defined in this same label. If this is done for all the input examples of the learning task (for all the labels $\sigma_t$, {\small $1\leq t\leq \tau$}), it means that the programmed action model $\Xi$ is compliant with all the input knowledge and hence, it is a solution to the action model learning task.
\end{proof}

\begin{figure}[hbt]
\begin{tiny}
\begin{verbatim}
(:action apply_stack
  :parameters (?o1 - object ?o2 - object)
  :precondition
   (and (or (not(pre_on_stack_v1_v1)) (on ?o1 ?o1))
        (or (not(pre_on_stack_v1_v2)) (on ?o1 ?o2))
        (or (not(pre_on_stack_v2_v1)) (on ?o2 ?o1))
        (or (not(pre_on_stack_v2_v2)) (on ?o2 ?o2))
        (or (not(pre_ontable_stack_v1)) (ontable ?o1))
        (or (not(pre_ontable_stack_v2)) (ontable ?o2))
        (or (not(pre_clear_stack_v1)) (clear ?o1))
        (or (not(pre_clear_stack_v2)) (clear ?o2))
        (or (not(pre_holding_stack_v1)) (holding ?o1))
        (or (not(pre_holding_stack_v2)) (holding ?o2))
        (or (not(pre_handempty_stack)) (handempty)))
  :effect
   (and (when (del_on_stack_v1_v1) (not(on ?o1 ?o1)))
        (when (del_on_stack_v1_v2) (not(on ?o1 ?o2)))
        (when (del_on_stack_v2_v1) (not(on ?o2 ?o1)))
        (when (del_on_stack_v2_v2) (not(on ?o2 ?o2)))
        (when (del_ontable_stack_v1) (not(ontable ?o1)))
        (when (del_ontable_stack_v2) (not (ontable ?o2)))
        (when (del_clear_stack_v1) (not (clear ?o1)))
        (when (del_clear_stack_v2) (not (clear ?o2)))
        (when (del_holding_stack_v1) (not (holding ?o1)))
        (when (del_holding_stack_v2) (not (holding ?o2)))
        (when (del_handempty_stack) (not (handempty)))
        (when (add_on_stack_v1_v1) (on ?o1 ?o1))
        (when (add_on_stack_v1_v2) (on ?o1 ?o2))
        (when (add_on_stack_v2_v1) (on ?o2 ?o1))
        (when (add_on_stack_v2_v2) (on ?o2 ?o2))
        (when (add_ontable_stack_v1) (ontable ?o1))
        (when (add_ontable_stack_v2) (ontable ?o2))
        (when (add_clear_stack_v1) (clear ?o1))
        (when (add_clear_stack_v2) (clear ?o2))
        (when (add_holding_stack_v1) (holding ?o1))
        (when (add_holding_stack_v2) (holding ?o2))
        (when (add_handempty_stack) (handempty))
        (when (modeProg) (not(modeProg)))))
\end{verbatim}
\end{tiny}
 \caption{\small Action for applying an already programmed operator schema $stack$ as encoded in PDDL.}
\label{fig:compilation}
\end{figure}

@@

\section{Evaluation}
We evaluated our learning approach for different amounts of available input knowledge. In all the experiments the classical planning instances resulting from our compilations are adressed by the SAT-based classical planner {\sc Madagascar}~\cite{rintanen2014madagascar} given its ability to deal with planning instances populated with dead-ends.

@@

\subsection{Learning action models from example plans}
Here we assess the performance of our learning approach when addressing the $\Lambda$ learning task. The quality of the learned models is quantified using the {\em precision} and {\em recall} metrics frequently used in {\em pattern recognition}~\cite{davis2006relationship}. This metrics are computed in the learned models with respect to the actual models taken as reference.

Table~\ref{tab:results_plans} summarizes the obtained results.

\begin{table}[hbt!]
	\begin{center}
		\begin{tabular}{l|l|l|l|l|l|l|}
			 & \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c|}{\bf Del}  \\ \cline{2-7}			 
			  & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
			\hline
			Blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Visitall & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Gripper & 1.0 & 0.6 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Miconic & 1.0 & 0.3 & 1.0 & 1.0 & 1.0 & 1.0 \\
			Floortile & 0.2 & 0.2 & 0.8 & 0.5 & 1.0 & 0.9 \\
			Pegsol & - & - & - & - & - & - \\
		\end{tabular}
	\end{center}
\label{tab:results_plans}	        
\caption{The {\em precision} and {\em recall} values achieved by the learned models in the different domains.}
\end{table}

\subsection{Learning action models from example states}
When the set of input planning task is not available, the planner determines also the actions that must satistying the input labels so actions can reformulated and still be compliant with the learning examples. For instance a blocksworld can be learned where the operator {\small\tt stack} is defined with the preconditions and effects of the {\small\tt unstack} operator and vice versa.

@@

This research opens the door to the bootstrapping of action model. That is that a planner collects by its own the data that it is necessary to define an action model for a given planning task. With this regard, collecting {\em informative} examples for learning planning action models is challenging open issue. Planning actions include preconditions that are only satisfied by specific sequences of actions, and often, with a low probability of being chosen by chance~\cite{fern2004learning}. The recent success of recent algorithms for exploring planning tasks~\cite{geffner:novelty:IJCAI17} motivates the development of novel approaches that do not assume that a learning set of plans is given apriori but instead, autonomously collect the learning examples.
